The \dealii{} Library, Version 9.2

### 2020-05-31 9.2/paper.tex
Added a first version of section 2.4 related t the support for particle-based methods

\author[3]{Bruno Blais}
\affil[3]{Research Unit for Industrial Flows Processes (URPEI),
          Polytechnique Montréal,
          PO Box 6079, Stn Centre-Ville, Montréal, Québec, Canada, H3C 3A7.
          {\texttt{bruno.blais@polymtl.ca}}}

@@

@@

>>>>

\author[3]{Bruno Blais}
\affil[3]{Research Unit for Industrial Flows Processes (URPEI), Department of Chemical Engineering,
          Polytechnique Montréal,
          PO Box 6079, Stn Centre-Ville, Montréal, Québec, Canada, H3C 3A7.
          {\texttt{bruno.blais@polymtl.ca}}}

@@

Support for particles was originally introduced in \dealii{} version 9.0. In \dealii,
particles can be used as passive tracers, or as part of more complex
models such as those based on Particle-In-Cells (PIC) approaches \cite{gassmoller2018flexible}.

With the current release, the support for particles has been further expanded: New parallel
 insertion mechanisms and a basic interface to post-process particles have
been added, effectively making their usage more flexible and enabling a larger
range of use cases (e.g. immersed boundaries in step-70).

Through the addition of the \texttt{Particles::ParticleHandler::insert\_global\_particles} member function,
 particles can now be inserted in parallel from a vector of points even if these points do not lie
 on the subdomain from which the insertion is called. This operation requires extensive 
 communication between the processes to locate   the MPI process the cell in which the particle
  is located. However, it is made significantly faster  through the usage of bounding boxes
  that surround the cells of each subdomain. 
  This function also takes care of transferring the properties attached to the particles to their new owner.
 This new capacity enables particle generators that insert particles at the location
 of the support points (\texttt{Particles::Generator::dof\_support\_points}) and at the quadrature points (\texttt{Particles::Generator::quadrature\_points}) of a
 possibly non-matching triangulation. Consequently, complex particle patterns can be inserted
 using unstructured hexahedral grids generated outside of \dealii{}.

To visualize the motion of particles, the \texttt{Particles::DataOut} class was added to the library.
In its current version, this class supports writing the particles positions and id in all format supported
by \dealii, but does not allow writing the properties attached to the particles.

@@

B.~Blais was partially supported by the National Science and Engineering Research Council of Canada(NSERC)  through the RGPIN-2020-04510 Discovery Grant
